A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-06-28 paper/main.tex
little changes in abstract

\todo{Wort zur Validierungsstudie; Es sind erst 110 von max 300 Worten verbraucht}
\thispagestyle{fancy}
\begin{abstract}
% up to 300 words
Here we present an annotation of speech in the audio-visual movie ``Forrest
Gump'' and its audio-description (i.e. the audio-only variant) as an addition to
a large public functional brain imaging dataset
(\href{www.studyforrest.org}{studyforrest.org}). The annotation provides
information about the exact timing of each of the more than 2.500 spoken
sentences, 16.000 words (including 202 non-speech vocalizations), 66.000
phonemes and their corresponding speaker. Additionally for every word, we
provide lemmatization, a simple part-of-speech-tagging putting words into 15
grammatical categories, a detailed part-of-speech tagging putting words into 43
grammatical categories, syntactic dependencies within each sentence, and a
semantic analysis based on word embeddings representing each word in a
300-dimensional semantic space. This annotation facilitates creating models of
brain activity related to processing spoken language under conditions of
real-life complexity.
\end{abstract}

>>>>

\todo{Wort zur Validierungsstudie; Es sind erst 110 von max 300 Worten
verbraucht} \thispagestyle{fancy} \begin{abstract}
% up to 300 words
Here we present an annotation of speech in the audio-visual movie ``Forrest
Gump'' and its audio-description (i.e. the audio-only variant of the movie) as
an addition to a large public functional brain imaging dataset
(\href{www.studyforrest.org}{studyforrest.org}). The annotation provides
information about the exact timing of each of the more than 2500 spoken
sentences, 16000 words (including 202 non-speech vocalizations), 66000 phonemes,
and their corresponding speaker. Additionally for every word, we provide
lemmatization, a simple part-of-speech-tagging (15 grammatical categories), a
detailed part-of-speech tagging (43 grammatical categories), syntactic
dependencies, and a semantic analysis based on word embeddings which represents
each word in a 300-dimensional semantic space. This annotation enables
researchers to create sophisticated models of brain activity related to
phonetics, grammar, syntax, and semantics under conditions of real-life
complexity.  \end{abstract}
